\scuba: iterative map-making with the Sub-Millimetre User Reduction Facility

### 2012-09-07 smurf_paper.tex
A further stab at the acknowledgements

The James Clerk Maxwell Telescope is operated by the Joint Astronomy
Centre on behalf of the Science and Technology Facilities Council of
the United Kingdom, the Netherlands Organisation for Scientific
Research, and the National Research Council of Canada. Additional
funds for the contruction of \scuba\ were provided by the Canada
Foundation for Innovation. EC thanks CANARIE/CANFAR for additional
funding. This research was supported in part by the Natural Sciences
and Engineering Research Council of Canada. ... general thanks to
people at JAC ... also explicitly mention Dennis, Alex and Jen ...

>>>>

The James Clerk Maxwell Telescope is operated by the Joint Astronomy
Centre on behalf of the Science and Technology Facilities Council of
the United Kingdom, the Netherlands Organisation for Scientific
Research, and the National Research Council of Canada. Additional
funds for the contruction of \scuba\ were provided by the Canada
Foundation for Innovation. EC thanks CANARIE/CANFAR for additional
funding. This research was supported in part by the Natural Sciences
and Engineering Research Council of Canada. The authors thank the
members of the SCUBA-2 commissioning team for testing the
map-maker and reporting anomalies; in particular Antonio Chrysostomou
and Jessica Dempsey. We also thank Dennis Kelly, Alex van Engelen and
Jennifer Balfour for work on the SCUBA-2 observation simulator;
and Mark Thompson, Craig Walther and S\'{e}verin Gaudet for being
on the Critical Design Review panel.
